\documentclass{bluefin_cv}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\name{Josh}{Finnie}
\position{Experienced Software Enginner}
\location{Charlotte, NC}
\phone{860-716-5996}
\email{josh@jfin.us}
\linkedin{joshfinnie}
\homepage{www.joshfinnie.com}

\begin{document}

% ------------------------------------------------------------------------------
% HEADER
% ------------------------------------------------------------------------------
\makeheader

% ------------------------------------------------------------------------------
% PROFESSIONAL STATEMENT
% ------------------------------------------------------------------------------
\section{Introduction}
\justify{
  With over 10 years of experience in software engineering, I specialize in building scalable APIs, interactive websites, and optimizing internal team processes.
  My career demonstrates a commitment to technical excellence, innovative problem-solving, and leadership in developing robust software solutions.
  I combine deep technical expertise with a passion for mentoring and process improvement, driving both project success and team growth.
}

% ------------------------------------------------------------------------------
% Technical Strengths
% ------------------------------------------------------------------------------
%\section{Technical Strengths}
%\hspace*{-0.25cm}
%\begin{tabular}{>{\bfseries}p{0.25\textwidth}p{0.70\textwidth}}
%  Backend Technology & Python, Node.js, Rust, Go \\
%  Frontend Technology & Javascript/Typescript, CSS, htmx \\
%  Databases & PostgreSQL, Redis, MongoDB, MySQL \\
%  Other Technologies & AWS, Docker, Pulumi, Terraform, Kubernetes, GraphQL \\
%\end{tabular}

%------------------------------------------------------------------------------
% PROFESSIONAL EXPERIENCE
%------------------------------------------------------------------------------
\section{Professional Experience}

\workexperience{Senior Software Engineer}{05/2023 - Present}{People Data Labs}
{
  Lead back-end engineer on the Delivery and API team, enhancing customer interactions with our data via API.
  Collaborate with engineering, data science, product, and other technical teams to build compliant, innovative, people-data-based software solutions.
}
{
  \item {\bf Bug Resolution}: Reduce customer complaints by 20\% within the first year by addressing issues raised by Customer Success and Product teams promptly.
  \item {\bf API Development}: Implement best practices significantly improved the existing Flask codebase, and deprecated an outdated Django codebase.
  \item {\bf Project Leadership}: Act as captain for monthly data update launches, coordinating efforts between the API team and the Data team to ensure seamless updates.
  \item {\bf SDK Development}: Helped develop and maintain the People Data Labs' SDKs. Wrote the Rust SDK in its entirety.
}
{
  Python,
  Pulumi,
  Docker,
  Rust,
  Go,
  AWS (RDS, Elasticache, Lambda, Batch)
}

\workexperience{Staff Software Engineer}{05/2022 - 03/2023}{IndigoAg}
{
  Contributed to Carbon by Indigo, a platform enabling farmers to earn income through sustainable practices leading to high-quality, registry-issued carbon credits.
  Collaborated with external partners to integrate their data into our carbon sequestration models.
}
{
  \item {\bf API Development}: Developed the next-generation Carbon Sequestration application API using Flask, working closely with stakeholders and the product team to deliver a robust solution.
  \item {\bf Project Leadership}: Led the process from initial architecture to final development, resulting in increased adoption of the carbon sequestration application.
  \item {\bf Mentorship}: Mentored junior developers and established best practices across the engineering department, fostering a culture of continuous improvement.
  \item {\bf Technical Documentation}: Authored comprehensive technical documentation to streamline company-wide data backfill procedures, enhancing overall operational efficiency.
  %\item Was part of the on-call rotation keeping the webapp running during crutial, heavy-load times.
}
{
  Python,
  AWS RDS,
  Javascript,
  Docker
}

\workexperience{Senior Software Engineer}{09/2019 - 05/2022}{PBS}
{
  Led development on PBS.org's backend, focusing on critical projects like device authentication and enhanced website search functionality, ensuring seamless user experiences.
}
{
  \item {\bf Legacy Modernization}: Modernized legacy Django applications by adding a comprehensive test suite, upgrading packages, and updating deployment infrastructure, significantly enhancing readability and security.
  \item {\bf GraphQL Architecture}: Led the development of a new GraphQL endpoint for content distribution, addressing the diverse needs of various teams and improving content delivery efficiency.
  \item {\bf Infrastructure Improvement}: Created a unified infrastructure framework for PBS Engineering, standardizing service deployment to AWS and streamlining operational processes.
  \item {\bf Code Quality Standards}: Developed cross-application best practices for code quality and testing infrastructure, ensuring high standards across all projects.
  %\item Thought Leadership: Acted as a thought leader for experimental changes, sharing insights and learnings through tech talks and presentations, fostering innovation within the engineering team.
  %\item Was a go-to generalist who helps brainstorm and fix cross-team architecture problems along with helping optimizing my team's overall workflow.
  %\item Ran weekly coding practices to better improve PBS Engineering's understanding of complex code issues.
}
{
  Python,
  Javascript,
  Go,
  CSS,
  PostgreSQL,
  Docker,
  GraphQL,
  AWS (ECS, ECR)
}

\workexperience{Senior Software Engineer}{10/2018 - 08/2019}{Skyword (Acquired TrackMaven)}
{
  Led the integration effort to unify users between the TrackMaven and Skyword platforms, implementing best practices for security upgrades to ensure a seamless and secure user experience.
}
{
  \item {\bf User Integration}: Led the effort to unify users between the TrackMaven and Skyword platforms by developing a unified login micro-service in Django, synchronizing authentication across both platforms.
  \item {\bf Security Enhancements}: Designed and implemented best practices for continuous security upgrades using Snyk, Dependabot, and GitHub Security Hub, ensuring the repositories remained secure and up-to-date.
  \item {\bf Cross-Platform Data Exchange}: Developed a robust data exchange system between TrackMaven’s Django infrastructure and Skyword’s Java infrastructure, facilitating seamless data flow between the two systems.
}
{
  Python,
  PostgreSQL,
  Redis,
  Docker,
  Kubernetes,
  Kotlin,
  AWS (full suite)
}

\workexperience{Software Engineer \(\rightarrow\) Senior Software Engineer}{03/2014 - 10/2018}{TrackMaven}
{
  Joined as the fourth engineer in a leading social media management company working with Fortune 500 companies to enhance their social media presence.
  Played a versatile role in both frontend and backend development.
}
{
  \item {\bf Python 3 Migration}: Led the architecture and execution of migrating the core Django application, upgrading all application dependencies to ensure compatibility and performance improvements.
  \item {\bf Kubernetes Infrastructure}: Co-led planning and architecture, introducing deployment best practices through Terraform, enhancing deployment efficiency and reliability.
  \item {\bf On-Call Leadership}: Served on the senior engineering team responsible for on-call triage and after-hours deployments, ensuring the stability and availability of multiple services.
  \item {\bf JavaScript Transition}: Developed testing protocols and best practices to support the successful transition of the live web application from CoffeeScript to modern JavaScript, improving code maintainability and performance.
  \item {\bf Quality and Infrastructure Team}: Established and led the team, focusing on promoting robust application infrastructure, high-quality code, and best practices across the engineering department.
  %\item Provided direct technical support to Software Maven team members and collaborative technical support to other departments within TrackMaven.
}
{
  Python,
  Javascript,
  PostgreSQL,
  Redis,
  Docker,
  Kubernetes,
  Terraform,
  AWS (full suite)
}

\workexperience{Application Developer}{02/2012 - 03/2014}{Koansys, LLC}
{
  As the first hire at an engineering consulting firm, contributed to multiple contracts, ranging from migrating software to current best practices to developing an Interactive Satellite Tracker (iSat) for Science@NASA.
}
{
  \item {\bf iSat Development}: Developed and deployed the Interactive Satellite Tracker (iSat), a JavaScript application that calculates real-time satellite positioning using open-source data for Science@NASA.
  %\item {\bf Application Maintenance}: Enhanced and maintained the iSat application to continually meet the evolving needs of Science@NASA.
  \item {\bf Cloud Migration}: Designed and built cloud infrastructure and automated migration scripts using Ansible, transitioning Science@NASA’s Content Management System from Django to Drupal and moving it to Amazon Web Services.
}
{
  Python,
  Javascript,
  Drupal,
  AWS (EC2, S3, Route53, Cloudfront, API Gateway)
}

%------------------------------------------------------------------------------
% PERSONAL PROJECTS
%------------------------------------------------------------------------------
%\section{Highlighted Personal Projects}

%\projectsubsection{wasm-frontmatter}{https://www.npmjs.com/package/wasm-frontmatter}
%\justify{A clone of grey-matter written in Rust. The project is used to generate Wasm code and is released on NPM. My tests have found that Wasm-Frontmatter is three times faster than the javascript equivalent.}

%\projectsubsection{PushFile}{https://www.npmjs.com/package/pushfile}
%\justify{A project written in Node.js which allows you to push a file to Amazon Web Services S3 and gives you an URL in return. Written using the latest TypeScript syntax and is compiled to ES5 so it works as a command line tool.}

%\projectsubsection{JoshFinnie.com}{https://www.joshfinnie.com}
%\justify{My personal blog written using the Astro.Build static site generator. It takes advantage of Tailwind CSS and is hosted on Netlify for high-availability. I write about my learnings in software development and tutorials.}

%\smallskip
%\centerline{\textsl{More open-source projects found at https://github.com/joshfinnie/}}

%------------------------------------------------------------------------------
% TALKS & PRESENTATIONS
%------------------------------------------------------------------------------
%\section{Talks \& Presentations}
%\begin{bfcvlist}
%  \item \bfcvtalk{Introduction to Python Poetry}{IndigoAg Internal Tech Talk}{February 1st, 2023}
%  \item \bfcvtalk{Introduction to Asynchronous Python}{IndigoAg Internal Tech Talk}{December 8th, 2022}
%  \item \bfcvtalk{gRPC Walkthrough and Programming Showcase}{PBS Internal Tech Talk}{June 23rd, 2021}
%  \item \bfcvtalk{Building Wasm-Frontmatter}{RustDC}{March 16, 2021}
%  \item \bfcvtalk{Intro to Rust and Wasm for Javascript Developers}{DC JS}{December 9, 2020}
%  \item \bfcvtalk{Docker Multi-stage Builds and other Best Practices}{PBS Internal Tech Talk}{July, 21, 2020}
%  \item \bfcvtalk{Docker's Best Practices}{Django District, etc.}{October 02, 2019}
%  \item \bfcvtalk{Kubernetes Overview Offsite}{Skyword Internal Talk}{May 10, 2019}
%  \item GraphQL Lunch \& Learn - \textsl{TrackMaven Internal Talk}, September 4, 2018
%  \item Flask, Zappa, and AWS Lambda - \textsl{Django District, etc.}, January 24, 2017
%  \item Decoupling our Angular.js App - \textsl{AngularJS DC}, October 19, 2016
%  \item Quick and Dirty AWS Lambda in Node.js - \textsl{NodeDC}, July 21, 2016
%  \item CoffeeScript and the Road to ES2015 - \textsl{JavaScript DC}, June 23, 2016
%\end{bfcvlist}
%\smallskip
%\centerline{\textsl{All talks and presentations found at https://www.joshfinnie.com/talks/}}

%------------------------------------------------------------------------------
% EDUCATION
%------------------------------------------------------------------------------
\section{Education}
\education{University of Maryland Global Campus}{M.S. in Data Analytics (Expected 2026)}
\education{Central Connecticut State University}{Classes towards a M.S. in Geography (GIS Track)}
\education{University of Connecticut}{B.A. in Economics. (Certificate in Quantitative Economics \& Minor in Mathematics)}

%------------------------------------------------------------------------------
% END OF FILE
%------------------------------------------------------------------------------
\end{document}
